Long groovy title goes here

### 2013-06-25 shanghai.tex
d+1 to d

We now say a few words about the commutative group schemes locally of
finite type over $\Fq$ that appear in our geometrization of admissible
characters of algebraic tori over local fields. Let $K$ be a
non-Archimedean local field with residual field $\Fq$; we place no
restrictions on the characteristic of $K$ -- in particular, it may be
$0$ or not. Write $\OK$ for ring of integers of $K$ and $\pK$ for the
maximal ideal in $\OK$.  Let $T$ be an algebraic torus defined over
$K$. Let $\TT$ be a N\'eron model for $T$; recall that this is a
smooth group scheme locally of finite type over $\OK$. For each
non-negative integer $d$, let $\GN{T}_d$ be the Greenberg transform of
$\TT \otimes \OK/\pK^{d+1}$; the commutative group scheme $\GN{T}_d$
plays the r\^{o}le of $G$, above.

@@

For each $d\in \NN$, let $\TT_{d}$ be the smooth group scheme over
$\OK/\pK^{d+1}$ obtained from $\TT$ by base change along $\OK \to
\OK/\pK^{d+1}$. Observe that $\OK/\pK^{d+1}$ is an Artin ring and
$\TT_{d}$ is locally of finite type over $\OK/\pK^{d+1}$.

Let $\GN{T}_{d}$ be the group scheme over $\Fq$ produced by applying
the Greenberg functor to $\TT_{d}$. (See \cite{Greenberg:2} and
\cite[Ch. 9, \S 6]{BLR} for background on the Greenberg functor.)
%Then $\GN{T}_d(\Fq) = \TT(\OK/\pK^{d+1})$.

\begin{proposition}\label{prop:GN}
  Fundamental properties of the group $\Fq$-scheme $\GN{T}_d$, for all $d\in \NN$:
  \begin{enumerate}
  \labitem{(GNd.0)}{GN0} $\GN{T}_d^0$, the identity component of
    $\GN{T}_d$, is a commutative algebraic group over $\Fq$;
  \labitem{(GNd.1)}{GNd} $\GN{T}_d$ is smooth and locally of finite type over $\Fq$;
  \labitem{(GNd.2)}{pi0} $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$;
  \labitem{(GNd.3)}{fg} the component group of $\GN{T}_d$ is geometrically finitely generated;
  \labitem{(GNd.4)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^{d+1})$, canonically;
\end{enumerate}
\end{proposition}

@@

%\input{application}
\begin{theorem}\label{thm:application}
  Let $T$ be an algebraic torus over a non-Archimdean local field $K$.
  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d\in \NN$, the
  Picard group of the category of character sheaves on $\GN{T}_d$ is
  canonically isomorphic to the group of characters of $T(K)$ of depth
  at most $d$:
  \[
  \CS(\GN{T}_d)_{/\text{iso}} \iso \Hom_{\leq d}(T(K),\EE^\times).
  \]
\end{theorem}

\begin{proof}
  By \ref{GNd} and \ref{fg}, we may apply Theorem~\ref{thm:snake} to
  $\GN{T}_d$ which provides a canonical isomorphism
  \[
  \CS(\GN{T}_d)_{/\text{iso}} \iso \Hom(\GN{T}_d(\Fq),\EE^\times).
  \]
  By \ref{dFq}, $\GN{T}_d(\Fq) \iso \TT(\OK/\pK^{d+1})$ canonically.
  To finish the proof we recall that the filtration of $T(K)$ used to
  define depth has the property that $\TT(\OK/\pK^{d+1}) \cong T(K) / T(K)_d$
  \cite[Prop 5.2]{Yu}.  Thus characters of $\GN{T}_d(\Fq)$ are
  in bijection with characters of $T(K)$ vanishing on $T(K)_d$.
\end{proof}

>>>>

We now say a few words about the commutative group schemes locally of
finite type over $\Fq$ that appear in our geometrization of admissible
characters of algebraic tori over local fields. Let $K$ be a
non-Archimedean local field with residual field $\Fq$; we place no
restrictions on the characteristic of $K$ -- in particular, it may be
$0$ or not. Write $\OK$ for ring of integers of $K$ and $\pK$ for the
maximal ideal in $\OK$.  Let $T$ be an algebraic torus defined over
$K$. Let $\TT$ be a N\'eron model for $T$; recall that this is a
smooth group scheme locally of finite type over $\OK$. For each
non-negative integer $d$, let $\GN{T}_d$ be the Greenberg transform of
$\TT \otimes \OK/\pK^d$; the commutative group scheme $\GN{T}_d$
plays the r\^{o}le of $G$, above.

@@

For each $d\in \ZZ_{>0}$, let $\TT_{d}$ be the smooth group scheme over
$\OK/\pK^d$ obtained from $\TT$ by base change along $\OK \to
\OK/\pK^d$. Observe that $\OK/\pK^d$ is an Artin ring and
$\TT_{d}$ is locally of finite type over $\OK/\pK^d$.

Let $\GN{T}_{d}$ be the group scheme over $\Fq$ produced by applying
the Greenberg functor to $\TT_{d}$. (See \cite{Greenberg:2} and
\cite[Ch. 9, \S 6]{BLR} for background on the Greenberg functor.)
%Then $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$.

\begin{proposition}\label{prop:GN}
  Fundamental properties of the group $\Fq$-scheme $\GN{T}_d$, for all $d\in \NN$:
  \begin{enumerate}
  \labitem{(GNd.0)}{GN0} $\GN{T}_d^0$, the identity component of
    $\GN{T}_d$, is a commutative algebraic group over $\Fq$;
  \labitem{(GNd.1)}{GNd} $\GN{T}_d$ is smooth and locally of finite type over $\Fq$;
  \labitem{(GNd.2)}{pi0} $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$;
  \labitem{(GNd.3)}{fg} the component group of $\GN{T}_d$ is geometrically finitely generated;
  \labitem{(GNd.4)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$, canonically;
\end{enumerate}
\end{proposition}

@@

%\input{application}
\begin{theorem}\label{thm:application}
  Let $T$ be an algebraic torus over a non-Archimdean local field $K$.
  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
  Picard group of the category of character sheaves on $\GN{T}_d$ is
  canonically isomorphic to the group of characters of $T(K)$ of depth
  less than $d$:
  \[
  \CS(\GN{T}_d)_{/\text{iso}} \iso \Hom_{< d}(T(K),\EE^\times).
  \]
\end{theorem}

\begin{proof}
  By \ref{GNd} and \ref{fg}, we may apply Theorem~\ref{thm:snake} to
  $\GN{T}_d$ which provides a canonical isomorphism
  \[
  \CS(\GN{T}_d)_{/\text{iso}} \iso \Hom(\GN{T}_d(\Fq),\EE^\times).
  \]
  By \ref{dFq}, $\GN{T}_d(\Fq) \iso \TT(\OK/\pK^d)$ canonically.
  To finish the proof we recall that the filtration of $T(K)$ used to
  define depth has the property that $\TT(\OK/\pK^d) \cong T(K) / T(K)_d$
  \cite[Prop 5.2]{Yu} for $d \in \ZZ_{>0}$.  Thus characters of $\GN{T}_d(\Fq)$ are
  in bijection with characters of $T(K)$ vanishing on $T(K)_d$.
\end{proof}
